## Khoi Tran - s4664074

***

# Assignment 2

***

### 1. Display the first 10 rows of the dataset using `kable()` function (1 marks). 
### 2. Using `skim()` display the summary of variables. 
### 3. Use `fct_reorder` and `parse_number` functions to create a factor variable `family_income`(2 mark).
### 4. What is the number of people who celebrate?
### 5. What are categories and insights for each main dish served and the method it is prepared?
### 6. Create 3 different data viz showing insights for main dish served and the method. Provide your own legend and use themes.
### 7. How many use cranberry sauce? How many use gravy?
### 8. What is the distribution of those who celebrate across income ranges. Create a data viz.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(skimr)

data <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-20/thanksgiving_meals.csv")

#predict income base on menu
#pick which variable is valued to your analysis
#use whole dataset a portion of it
#regression (predict number or category): letter -> number/ parse_number(family_income)
#filer NA variable when predict category
#select(-) exclude column

```

