## Khoi Tran - s4664074

***

# Assignment 2

***

### 1. Display the first 10 rows of the dataset using `kable()` function
```{r}
#Loading library
library(tidyverse)
library(skimr)
library(randomForest)
library(knitr)
library(scales)
library(lubridate)
library(widyr)

#Import dataset
meals <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-20/thanksgiving_meals.csv")

kable(meals[1:10,])
```
### 2. Using `skim()` display the summary of variables. Think about the task to predict a family income based on their menu: what variables may be useful? Are all of them correct type? Write 2-3 sentences with your explanation. (2 marks) 
```{r}
skim(meals)

# To predict a family income (numeric variable) based on their menu, we could use "age" variable or "kids_table_age" variable to predict "family_income" variable. All of them are character type, so we will need to transform them into numeric type.

# TO predict a community type or US_region (category variables) based on their menu, we could use different variables such as "main_dish", "celebrate", "main_prep", "gender", "age", "family_income", "kids_table_age". All of them are character type, which we can transform them into category type. 
```
### 3. Use `fct_reorder` and `parse_number` functions to create a factor variable `family_income`
```{r}
meals_income_factor <- meals %>%
  filter(!is.na(family_income) & family_income != "Prefer not to answer") %>%
  mutate(family_income = fct_reorder(as_factor(family_income), parse_number(family_income)))

class(meals_income_factor$family_income)
```
### 4. What is the number of people who celebrate?
```{r}
meals %>% count(celebrate)
#There are 980 people who celebrate thanksgiving
```
### 5. What are categories and insights for each main dish served and the method it is prepared?
```{r}
meals %>% count(main_dish, main_prep, sort = TRUE)
# If there is no main dish, there would be no main prep as well

meals_main <- meals %>% 
  filter( main_dish != "I don't know" & #unidentified variable
          main_dish != "Tofurkey" &     #mistype
          main_dish != "Turducken" &    #mistype
          main_prep != "I don't know" &
          !is.na(main_dish) & 
          !is.na(main_prep))

meals_main %>% count(main_dish, sort = TRUE)
meals_main %>% count(main_prep, sort = TRUE)

# There are four main dishes (Turkey, Ham/Pork, Chicken, Roast beef) during Thanksgiving, in which they can be mainly prepared in three different ways (Baked, Roasted, Fried). 
```
### 6. Create 3 different data viz showing insights for main dish served and the method. Provide your own legend and use themes.
```{r}
theme_set(theme_light())

meals_main %>% ggplot(
  aes(main_dish)
)+
  geom_bar() +
  coord_flip() +
  labs(x="Main Dish", y="Number of Observations")
#Out of 5 categories, the graph indicates that Turkey is the most popular main dish during thanksgiving with over 750 observations while chicken and roast beef are the least favorite  

meals_main %>% ggplot(
  aes(x=main_prep)
)+
  geom_bar() +
  coord_flip() +
  labs(x="Main Prep", y="Number of Observations")
#Out of 4 categories, the graph indicates that baking is the most favorite preparation method for main dish, following that is the roasting method

meals_main %>% 
  group_by(main_dish, main_prep) %>% 
  summarise(n=n()) %>%
  ungroup() %>%
  ggplot(
    aes(x=main_dish, 
        y=n,
        fill=main_prep)
  )+
  geom_col() +
  labs(x="Main Dish", y="Number of Observations") +
  coord_flip()+
  facet_wrap(~main_prep, nrow=2) 
# For Turkey dish, most people prefer baking rather that roasting, Some people also enjoy fried turkey or they choose different methods for preparation 
```
### 7. How many use cranberry sauce? How many use gravy?
```{r}
meals %>% count(main_dish, cranberry, gravy)
# If there is no main dish, there would be no cranberry sauce as well gravy

meals_main %>% count(cranberry)
# There is total 802 observations of people who use cranberry sauce, including 24 people specify other

meals_main %>% count(gravy)
# There are 866 people who use gravy
```
### 8. What is the distribution of those who celebrate across income ranges. Create a data viz.
```{r}
meals_income_factor %>% count(family_income, sort = TRUE)
meals_income_factor %>%
  #mutate(family_income = fct_lump(family_income, 6, other_level = "$125,000 to $199,999" ), sort = TRUE) %>%
  group_by(family_income, celebrate) %>%
  summarise(n=n()) %>%
  mutate(family_income = fct_reorder(family_income, -n)) %>%
  ggplot(
  aes(x=family_income,
      y=n,
      fill=celebrate)
  )+
  geom_col()+
  labs(x="family income", y="Number of Observations")+
  coord_flip()+
  facet_wrap(~celebrate, nrow=2)

# Majority of people who celebrate Thanksgiving have the family income range from $25,000 to $125,000 with most of them have $25,000 to $50,000. Any people have the family income less than $25,000 or more than $125,000 are less likely to celebrate Thanksgiving, except people who have family income more than $200,000.
```
### 10. Use the following code to create a new data set (2 mark). Write 2-3 sentences with your explanation of what it does.(4 marks)
```{r}
meals_type_value <- meals %>% 
  select(id, starts_with("side"),
         starts_with("pie"),
         starts_with("dessert")) %>% 
  select(-side15, -pie13, -dessert12) %>% 
  gather(type, value, -id) %>% 
  filter(!is.na(value),
         !value %in% c("None", "Other (please specify)")) %>% 
  mutate(type = str_remove(type, "\\d+")) 

# In the meals dataset, select column "id" and all the columns stars with word "side", "pie" or "dessert". After that, dropping or excluding columns "side15", "pie13" and "dessert12". Then gather all variables (column's name) and its related values, excluding "id" variable, then put into "type" column (key column) and "value" column (value column) respectively. Next, filter out any values that is NA in "value" column and any values in the dataset that is specified in "c" category. Finally, remove any digit in "type" variable and add that back to new variable called "type".
```
### 11. Intall package `widyr` and use `pairwise_cor()` function https://www.rdocumentation.org/packages/widyr/versions/0.1.3/topics/pairwise_cor. Write 2-3 sentences with your explanation of what it does. (2 marks). Use this code for the new dataset `pairwise_cor(value, id, sort = TRUE)` Write 1 sentence with your explanation of what insights it shows. (2 marks)
```{r}
# 'pairwise_cor()' function find if there is any correlation or relationship (positive/negative) between 2 items in a column, in which they share the same values in another column (feature column). The value column helps decide which variable will be used in finding the correlation between two items.  

meals_type_value %>% pairwise_cor(value, id, sort = TRUE)

# It shows the correlation between any 2 items in "value" variables which share the same "id" feature. For example, the correlation between cookies and brownies is 0.41, which means that cookies and brownies has a positive relationship and change together at a rate of 0.41  
```
### 13. Use `lm()` or `randomForest()` function to build a model that predict a family income based on data in the dataset (8 marks). Compare 3 models using different set of input variables. Use different number of variables. Explaiin your choice of variables (3 sentences). Write 2 sentences explaining which model os best.
```{r}
meals_income_num <- meals %>% 
  filter(!is.na(family_income) & family_income != "Prefer not to answer") %>%
  mutate(family_income_num = parse_number(family_income))

randomForest(family_income_num~celebrate + main_dish + main_prep, data=meals_income_num, na.action = na.omit)
randomForest(family_income_num~gender + age + gravy + us_region, data=meals_income_num, na.action = na.omit)
randomForest(family_income_num~celebrate + main_dish + main_prep + us_region + gravy, data=meals_income_num, na.action = na.omit)

#

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


