---
title: "Assessment 1.1"
author: "Khoi Tran - s4664074"
date: "16/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## RMarkdown editing
### Overview
R Markdown documents provide ***quick, reproducible reporting*** from R. You write your document in markdown and embed executable R code chunks with the knitr syntax. You can update your document at any time by re-knitting the code chunks. You can then convert your document into several common formats.

[Markdown Basics](https://rmarkdown.rstudio.com/lesson-8.html)

```{r}
#Loading Packages
library(tidyverse)
library(skimr)

fastfood <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')

write_csv(fastfood,'fastfood_data.csv')

fastfood %>% glimpse()
fastfood %>% skim()

fastfood %>% head(10)
```

=======
R Markdown documents provide ***quick, reproducible reporting*** from R. You write your document in markdown and embed executable R code chunks with the knitr syntax. You can update your document at any time by re-knitting the code chunks. You can then convert your document into several common formats
>>>>>>> 74111b14dd73ef840fe63054178d9c7424afb192
