---
title: "Assessment 1.1"
author: "Khoi Tran - s4664074"
date: "16/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## RMarkdown editing
### Overview
R Markdown documents provide ***quick, reproducible reporting*** from R. You write your document in markdown and embed executable R code chunks with the knitr syntax. You can update your document at any time by re-knitting the code chunks. You can then convert your document into several common formats.

[Markdown Basics](https://rmarkdown.rstudio.com/lesson-8.html)


### Part 1
```{r}
#Loading Packages
library(tidyverse)
library(knitr)
library(skimr)
library(scales)
library(lubridate)

#Create variable with dataset
fastfood <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')

#Display the first 10 rows of the dataset
fastfood %>% 
  head(10) 

#Display the first 10 rows of the dataset and the first 5 variables (columns)
kable(head(fastfood[1:10,1:5])) 

#Display the observations that has more than 1000 calories
fastfood %>% 
  filter(calories > 1000) 

#Save observations with more than 40 in total_fat and more than 80 in total_carb

dont_eat_this <- fastfood %>% 
  filter(total_fat > 40) %>%
  filter(total_carb > 80)
#fastfood %>% 
  #filter(total_fat > 40 & total_carb > 80)

#Display observations from restaurant Mcdonalds
fastfood %>%
  filter(restaurant == "Mcdonalds")

```

### Part 2
```{r}
# Display the types of variables in the dataset using `skimr` package
skim(fastfood)

# Show the count of observations for each restaurant. 
fastfood %>% 
  count(restaurant)

# Using grouppings (group_by()), summarise and display the average number of calories for each restaurant.
fastfood %>%
  group_by(restaurant) %>%
  summarise(average_cal = mean(calories))

# Add a variable to the dataset, which calculates the average calories per type of restaurant and call it `average_calories` 
fastfood %>%
  group_by(restaurant) %>%
  mutate(average_calories = mean(calories))

# Display the data vis of total fat per each type of restaurant. Write a narration (2-3 sentences) why you believe this type of data viz presents such information best. **
theme_set(theme_light())

fastfood %>% ggplot(
  aes(x=reorder(restaurant, -total_fat), 
      y=total_fat)
)+
  geom_col() +
  labs(x="Restaurant", 
       y="Total Fats", 
       title="Total Fat Per Each Type Of Restaurant"
       )+
  coord_flip()
```

Based on the menu of each restaurants, Burger king has the highest total fat in their menu compares to Chick Fil-A, which has the lowest total fat. Taco Bell's menu just slightly under Burger King in total fat, while Subway, McDonalds and Sonic have relatively same amount of total fat in their menu.

```{r}
# Add a variable to the dataset, which calculates the maximum total fat per type of restaurant and call it `max_total_fat` 
fastfood %>%
  group_by(restaurant) %>%
  mutate(max_total_fat = max(total_fat))

# Use observations for Mcdonalds to plot sugar variable against protein with `geom_point()` 
fastfood %>%
  filter(restaurant == "Mcdonalds") %>% 
  ggplot(
  aes(x=sugar,
      y=protein)
)+
  geom_point()
```
### Part 3




