---
title: "Assessment 1.1"
author: "Khoi Tran - s4664074"
date: "16/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## RMarkdown editing
### Overview
R Markdown documents provide ***quick, reproducible reporting*** from R. You write your document in markdown and embed executable R code chunks with the knitr syntax. You can update your document at any time by re-knitting the code chunks. You can then convert your document into several common formats.

[Markdown Basics](https://rmarkdown.rstudio.com/lesson-8.html)


### Part 1
```{r}
#Loading Packages
library(tidyverse)
library(knitr)
library(skimr)
library(scales)
library(lubridate)


#Create variable with dataset
fastfood <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')

#Display the first 10 rows of the dataset
fastfood %>% 
  head(10) 

#Display the first 10 rows of the dataset and the first 5 variables (columns)
kable(fastfood[1:10,1:5])

#Display the observations that has more than 1000 calories
fastfood %>% 
  filter(calories > 1000) 

#Save observations with more than 40 in total_fat and more than 80 in total_carb
dont_eat_this <- fastfood %>% 
  filter(total_fat > 40 & total_carb > 80)

#Display observations from restaurant Mcdonalds
fastfood %>%
  filter(restaurant == "Mcdonalds")

```

### Part 2
```{r}
# Display the types of variables in the dataset using `skimr` package
skim(fastfood)

# Show the count of observations for each restaurant. 
fastfood %>% 
  count(restaurant)

# Using grouppings (group_by()), summarise and display the average number of calories for each restaurant.
fastfood %>%
  group_by(restaurant) %>%
  summarise(average_cal = mean(calories)) %>%
  ungroup()

# Add a variable to the dataset, which calculates the average calories per type of restaurant and call it `average_calories` 
fastfood <- fastfood %>%
  group_by(restaurant) %>%
  mutate(average_calories = mean(calories)) %>%
  ungroup()

# Display the data vis of total fat per each type of restaurant. Write a narration (2-3 sentences) why you believe this type of data viz presents such information best. **
theme_set(theme_light())

fastfood %>% ggplot(
  aes(x=reorder(restaurant, -total_fat), 
      y=total_fat)
)+
  geom_col() +
  labs(x="Restaurant", 
       y="Total Fats", 
       title="Total Fat Per Each Type Of Restaurant"
       )

```

This column graph present such information best, because we have two variables: "restaurant" which is a discrete or catagory variable, while "total_fat" is a continuous (numeric) variable with differents values.

```{r}
# Add a variable to the dataset, which calculates the maximum total fat per type of restaurant and call it `max_total_fat` 
fastfood <- fastfood %>%
  group_by(restaurant) %>%
  mutate(max_total_fat = max(total_fat)) %>%
  ungroup()

# Use observations for Mcdonalds to plot sugar variable against protein with `geom_point()` 
fastfood %>%
  filter(restaurant == "Mcdonalds") %>% 
  ggplot(
  aes(x=sugar,
      y=protein)
)+
  geom_point()
```
### Part 3
```{r}
# Identify variable(s) which should be factors and transform their type into a factor variable.
fastfood <- fastfood %>%
  group_by(restaurant) %>%
  mutate(restaurant=as_factor(restaurant)) %>%
  ungroup()

# Use `calories` variable for `cut_number()` function to split it into 3 categories `n=3`, add labels `labels=c("low", "med", "high")` and make the dataset ordered. 
fastfood <- fastfood %>% 
  mutate(calories_type=cut_number(calories, n=3, labels=c("low", "med", "high"))) %>%
  group_by(restaurant) %>%
  arrange(desc(calories), .by_group = TRUE) %>%
  ungroup()

#Create a dataviz that shows the distribution of `calories_type` in food items for each type of restaurant. Think carefully about the choice of data viz. Use facets, coordinates and theme layers to make your data viz visually appealing and meaningful. Use factors related data viz functions.
fastfood %>% 
  group_by(restaurant, calories_type) %>% 
  summarise(n=n()) %>%
  ungroup() %>%
  mutate(restaurant = fct_reorder(restaurant, -n)) %>%
  ggplot(
  aes(x=restaurant,
      y=n,
      fill=calories_type)
)+
  geom_col()+
  labs(x="Restaurant", y="Number of food items")+
  coord_flip()+
  facet_wrap(~calories_type, nrow=1)

# The second variable should show the percentage of `trans_fat` in `total_fat`. Add the variable to the dataset and call it `trans_fat_percent`. Do not forget to save the updated dataset. 
fastfood <- fastfood %>%
  mutate(trans_fat_percent= round(((trans_fat/total_fat)*100),2))

# Create a dataviz that shows the distribution of `trans_fat` in food items for each type of restaurant. Think carefully about the choice of data viz. Use facets, coordinates and theme layers to make your data viz visually appealing and meaningful.
fastfood %>%
  filter(!is.na(trans_fat)) %>%
  mutate(trans_fat=as_factor(trans_fat)) %>%
  mutate(trans_fat = fct_lump(trans_fat, 5, other_level = "Over 2"), sort = TRUE) %>%
  group_by(restaurant, trans_fat) %>%
  summarise(n=n()) %>%
  mutate(restaurant = fct_reorder(restaurant, -n)) %>%
  ggplot(
  aes(x=restaurant,
      y=n,
      fill=trans_fat)
  )+
  geom_col()+
  labs(x="Restaurant", y="Number of food items")+
  coord_flip()+
  facet_wrap(~trans_fat, nrow=2)

# Calculate and show the average (mean)  `total_fat` for each type of restaurant. No need to save it as a variable.
fastfood %>%
  mutate(average_total_fat=mean(total_fat)) %>%

# And create a dataviz that allow to compare different restaurants on this variable (`total_fat`). You can present it on one dataviz (= no facets). 
  mutate(restaurant = fct_reorder(restaurant, -average_total_fat)) %>%
  ggplot(
    aes(x=restaurant,
        y=average_total_fat)
  )+
  geom_col()+
  labs(x="Restaurant", 
       y="Average Total Fat", 
       title="Average Total Fat Per Each Type Of Restaurant"
       ) 
```



